---
title: "Lab 04 - La Quinta is Spanish for next to Denny's, Pt. 1"
author: "Benjamin Egan"
date: "2/5"
output: github_document
---

### Load packages and data

```{r load-packages, message = FALSE, echo = FALSE}
library(tidyverse) 
library(dsbox) 
```

```{r load-data, message = FALSE, echo = FALSE}
states <- read_csv("data/states.csv")
```

### Exercise 1

```{r examine denny's dataset}

dennys %>%
  nrow()
dennys %>%
ncol()

```
There are 1,643 rows and 6 columns in the Denny's dataset

### Exercise 2

```{r examine La Quinta dataset}

laquinta %>%
  nrow()
laquinta %>%
ncol()

```
There are 909 rows and 6 columns in the La Quinta dataset

### Exercise 3

Based on the website, Denny's is only based in the United States (if I google it, apparently there are a handful of Denny's located in Canada, Mexico, etc.). For La Quinta, there are several hotels in China, New Zealand, Turkey, the United Arab Emirates, Chile, Colombia, and Ecquador.
...

### Exercise 4

...

### Exercise 5

...

### Exercise 6

...

 
Add exercise headings as needed.

